---
title: "Preprocessing Bank Marketing Data"
author: "Crupanshu Ashishbhai Udani, Karan Jeeten Thakkar"
date: "09/05/20"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo=TRUE,warning = FALSE,message=FALSE)
```

## Importing libraries
```{r Importing Library}
library(dplyr)# Used for easier data manipulation
library(caret)# Used for finding correlated attributes
library(rpart)# Used for decision tree
library(rpart.plot)# Used for ploting decision tree
print("All Libraries loaded")
```
## Reading the dataset
```{r Importing Dataset}
dataset <- read.csv('../data/bank-additional-full.csv',header = TRUE,sep = ';',na.strings = c("","NA","unknown"))
summary(dataset)
```
# 1. Preprocessing data
## 1.1 Cleaning Data
As a part of this step we'll be removing all the rows that contain NA values ( i.e. unknown in original dataset).
```{r}
data <- na.omit(dataset)
dim(data)
```
## 1.2 Exploring Data
As a part of this step we would be exploring each data field and checking the values.

#### Age:
```{r Age}
data$age<-as.integer(data$age)
barplot(table(data$age))
boxplot(data$age,horizontal = T,xlab = "Age",main="Box plot of Age distributution")
#abline(v=37.00,col="lightgrey")
#text(37, 10, "37.00", col = "darkgrey")
```

Summary: Age data is mostly skewed towards lower,middle age groups thus older age group could cause issue in the model.

#### Job
```{r Job, fig.width = 15}
job <- table(data$y,data$job)
barplot(job,names.arg = names(job),legend.text = c("no in  y","yes in y"),xlab = "Job",ylab = "Count")
```

#### Marital
```{r Marital}
marital <- table(data$y,data$marital)
barplot(marital,legend.text = c("no in  y","yes in y"))
```

#### Education
```{r Education, fig.width = 15}
education <- table(data$y,data$education)
barplot(education, legend.text = c("no in  y","yes in y"))
```

As per graph and data clearly for education *illiterate* has very low no of row of data (only **`r data %>% filter(education == "illiterate") %>% count()`**).

#### Default
```{r Default Field}
table(data$default)
```

Clearly for attribute *default* has only `r filter(data,default=="yes") %>% count()` rows with yes field. So the field would not be useful. Therefore the field can be dropped.

#### Housing
```{r housing}
housing <- table(data$y,data$housing)
barplot(housing,legend.text = c("no in  y","yes in y"),xlab = "Housing",ylab = "Frequency")
```

#### Loan
```{r loan}
loan <- table(data$y,data$loan)
barplot(loan,xlab = "Loan",ylab = "Frequency",legend.text = c("no in  y","yes in y"))
```

#### Contact
```{r Contact}
contact <- table(data$y,data$contact)
barplot(contact,xlab = "Contact",ylab = "Frequency",legend.text = c("no in  y","yes in y"))
```

#### Month
```{r Month}
month <- table(data$y,data$month)
barplot(month,xlab = "Month",ylab = "Frequency",legend.text = c("no in  y","yes in y"))
```

#### Day of Week
```{r Day of Week}
day_of_week <- table(data$y,data$day_of_week)
barplot(day_of_week,xlab = "Day of Week",ylab = "Frequency",legend.text = c("no in  y","yes in y"))
```

#### Duration
```{r Duration}
duration <- table(data$duration)
barplot(duration,xlab = "Duration",ylab = "Frequency")
boxplot(data$duration,horizontal = T)
```

The above plots clearly shows that there are more number of calls that has happened for shorted duration then larger duration.

#### Campaign
```{r Campaign}
data$campaign <- as.integer(data$campaign)
campaign <- table(data$y,data$campaign)
barplot(campaign,xlab = "Campaign",ylab = "Frequency",legend.text = c("no in  y","yes in y"))
```

The above plot clearly shows there is more data for campaign with less contact and very less data with more contacts done.

#### pdays
```{r pDays,fig.width = 12}
data$pdays<-as.integer(data$pdays)
pdaysCount <- table(data$pdays)
barplot(table(data$pdays),xlab = "pdays",ylab = "Frequency")
data %>% select(pdays) %>% filter(pdays == 999) %>% count()
```

#### Previous
```{r Previous }
data$previous <- as.integer(data$previous)
previous <- table(data$y,data$previous)
barplot(previous,xlab = "Previous",ylab = "Frequency",legend.text = c("no in  y","yes in y"))
```

#### pOutcome
```{r pOutcome}
poutcome <- table(data$y,data$poutcome)
barplot(poutcome,xlab = "poutcome",ylab = "Frequency",legend.text = c("no in  y","yes in y"))
plot(poutcome,main = "Mosaic plot of poutcome and y values",xlab = "y",ylab = "poutcome")
```

#### Social and Economical Context
```{r Social & Economical attribute, fig.width = 12}
## emp.var.rate
emp.var.rate <- table(data$y,data$emp.var.rate)
barplot(emp.var.rate,xlab = "emp.var.rate",ylab = "Frequency",legend.text = c("no in  y","yes in y"))
boxplot(data$emp.var.rate,horizontal = T,main ="Box plot of emp.var.rate")
## cons.price.idx
cons.price.idx <- table(data$y,data$cons.price.idx)
barplot(cons.price.idx,xlab = "cons.price.idx",ylab = "Frequency",legend.text = c("no in  y","yes in y"))
boxplot(data$emp.var.rate,horizontal = T,main ="Box plot of cons.price.idx")
## cons.conf.idx
cons.conf.idx <- table(data$y,data$cons.conf.idx)
barplot(cons.conf.idx,xlab = "cons.conf.idx",ylab = "Frequency",legend.text = c("no in  y","yes in y"))
boxplot(data$emp.var.rate,horizontal = T,main ="Box plot of cons.conf.idx")
## euribor3m
euribor3m <- table(data$euribor3m)
barplot(euribor3m,xlab = "euribor3m",ylab = "Frequency")
boxplot(data$euribor3m,horizontal = T,main ="Box plot of euribor3m")
## nr.employed
nr.employed <- table(data$y,data$nr.employed)
barplot(nr.employed,xlab = "nr.employed",ylab = "Frequency",legend.text = c("no in  y","yes in y"))
boxplot(data$nr.employed,horizontal = T,main ="Box plot of nr.employed")
```

## 1.3 Changing the categorical/logical data to factors
```{r}
data$job<-as.factor(data$job)
data$marital<-as.factor(data$marital)
data$education<-as.factor(data$education)
data$default<-as.factor(data$default)
data$housing<-as.factor(data$housing)
data$loan<-as.factor(data$loan)
data$contact<-as.factor(data$contact)
data$month<-as.factor(data$month)
data$day_of_week<-as.factor(data$day_of_week)
data$poutcome<-as.factor(data$poutcome)
data$y<-as.logical(data$y=="yes")
```

## 1.4 Checking Similarity of attributes using variance and correlation
```{r}
X <- subset(data,select = age:nr.employed) %>% data.matrix()
Y <- data$y
var_X <- var(X)
cor_X <- cor(X,method = "pearson")
print(var_X)
print(cor_X)
print(findCorrelation(cor_X,cutoff=0.9,names = T))
```
Based on similarity matrix we observe that field **emp.var.rate** and **euribor3m** are highly correlated and seemed redundant.


## 1.5 Dimensionality Reduction using PCA (Principle Component Analysis)
```{r Dimensionality Reduction 1}
pca_data<-prcomp(X,center = TRUE,scale. = TRUE)
data_pc<-pca_data$x
pca_rotation<-pca_data$rotation
summary(pca_data)
plot(pca_data)
```
```{r,,fig.width = 12, fig.height = 12}
biplot(pca_data)
sort(abs(pca_rotation[,1]))
```

Based on the summary of pca components, we observe that at about 6 components determines 50% of result and about 15 components describes 95% of result (based on Cumulative Proportion).
Further more as per the biplot we can clearly observe that our previous observation that field *emp.var.rate* and *euribor3m* are highly correlated.
Based on PC1 values of PCA analysis *loan* and *default* are the least contributing attributes.


## 1.6 Sampling Dataset
```{r}
set.seed(110) # Team 11
dataSampleindex <- sample(1:nrow(data),10000)
sampled_data <- data[dataSampleindex, ]
dim(sampled_data)
sampled_data$y <- as.factor(sampled_data$y)
```

```{r CleanWS, include = FALSE}
### Clean Env and Packages data
#rm(list= ls())
```

# 2. Classification
## 2.1 Splitting into training and test sets
### 2.1.1 Full sampled set benchmark 80:20 ,50:50
#### Naive Bayesian 80:20
```{r All columns - 80:20}
indxTrain80 <- createDataPartition(y = sampled_data$y,p = 0.80,list = FALSE)
training_all_col80 <- sampled_data[indxTrain80,]
testing_all_col80 <- sampled_data[-indxTrain80,]
x <- training_all_col80[, -21]
y <- training_all_col80$y
model <- train(x, y, 'nb', trControl=trainControl(method='cv', number=10))
Predict <- predict(model, newdata = testing_all_col80)
confusionMatrix(Predict, testing_all_col80$y,positive = "TRUE",mode = "prec_recall")
attributeImp <- varImp(model)
plot(attributeImp)
```

#### Naive Bayesian 50:50
```{r All columns - 50:50}
indxTrain50 <- createDataPartition(y = sampled_data$y,p = 0.50,list = FALSE)
training_all_col50 <- sampled_data[indxTrain50,]
testing_all_col50 <- sampled_data[-indxTrain50,]
x <- training_all_col50[, -21]
y <- training_all_col50$y
model <- train(x, y, 'nb', trControl=trainControl(method='cv', number=10))
Predict <- predict(model, newdata = testing_all_col50)
confusionMatrix(Predict, testing_all_col50$y,positive = "TRUE",mode = "prec_recall")
attributeImp <- varImp(model)
plot(attributeImp)
```

#### Decision Tree
##### With GINI Index 80:20
```{r}
fit <- rpart(formula = y ~ .,data = training_all_col80,method = "class")
rpart.plot(fit)
y_pred <- predict(fit,testing_all_col80,type = "class")
confMatrix <- confusionMatrix(y_pred,testing_all_col80$y,positive = "TRUE",mode="prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
attrImp <- varImp(fit)
plot(attributeImp)
```

##### With GINI Index 50:50
```{r}
fit <- rpart(formula = y ~ .,data = training_all_col50,method = "class")
rpart.plot(fit)
y_pred <- predict(fit,testing_all_col50,type = "class")
confMatrix <- confusionMatrix(y_pred,testing_all_col50$y,positive = "TRUE",mode="prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
attrImp <- varImp(fit)
plot(attributeImp)
```

##### With Information Gain 80:20
```{r}
fit <- rpart(formula = y ~ .,data = training_all_col80,method = "class",parms = list(split="information"))
rpart.plot(fit)
y_pred <- predict(fit,testing_all_col80,type = "class")
confMatrix <- confusionMatrix(y_pred,testing_all_col80$y,positive = "TRUE",mode="prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
attrImp <- varImp(fit)
plot(attributeImp)
```

##### With Information Gain 50:50
```{r}
fit <- rpart(formula = y ~ .,data = training_all_col80,method = "class",parms = list(split="information"))
rpart.plot(fit)
y_pred <- predict(fit,testing_all_col80,type = "class")
confMatrix <- confusionMatrix(y_pred,testing_all_col80$y,positive = "TRUE",mode="prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
attrImp <- varImp(fit)
plot(attributeImp)
```

### 2.1.2 Keep duration - drop pdays & loan & default - 70:30
```{r Keep duration - drop pdays & loan & default - 70:30}
indxTrain70 <- createDataPartition(y = sampled_data$y,p = 0.70,list = FALSE)
sample_data_with_dur_3_dropped_70 <- sampled_data
sample_data_with_dur_3_dropped_70[, c('pdays', 'loan', 'default')] <- list(NULL)
training_with_dur_3dropped_col70 <- sample_data_with_dur_3_dropped_70[indxTrain70,]
testing_with_dur_3dropped_col70 <- sample_data_with_dur_3_dropped_70[-indxTrain70,]
```

### 2.1.3 Drop duration - drop pdays & loan & default - 70:30
```{r Drop duration - drop pdays & loan & default - 70:30}
sample_data_without_dur_3_dropped_70 <- sampled_data
sample_data_without_dur_3_dropped_70[, c('pdays', 'loan', 'default', 'duration')] <- list(NULL)
training_without_dur_3dropped_col70 <- sample_data_without_dur_3_dropped_70[indxTrain70,]
testing_without_dur_3dropped_col70 <- sample_data_without_dur_3_dropped_70[-indxTrain70,]
```

### 2.1.4 Keep duration - drop pdays & loan & default & emp.var.rate - 70:30
```{r Keep duration - drop pdays & loan & default & emp.var.rate - 70:30}
sample_data_with_dur_4_dropped_70 <- sampled_data
sample_data_with_dur_4_dropped_70[, c('pdays', 'loan', 'default', 'emp.var.rate')] <- list(NULL)
training_with_dur_4dropped_col70 <- sample_data_with_dur_4_dropped_70[indxTrain70,]
testing_with_dur_4dropped_col70 <- sample_data_with_dur_4_dropped_70[-indxTrain70,]
```

### 2.1.5 Drop duration - drop pdays & loan & default & emp.var.rate - 70:30
```{r Drop duration - drop pdays & loan & default & emp.var.rate - 70:30}
sample_data_without_dur_4_dropped_70 <- sampled_data
sample_data_without_dur_4_dropped_70[, c('pdays', 'loan', 'default', 'emp.var.rate', 'duration')] <- list(NULL)
training_without_dur_4dropped_col70 <- sample_data_without_dur_4_dropped_70[indxTrain70,]
testing_without_dur_4dropped_col70 <- sample_data_without_dur_4_dropped_70[-indxTrain70,]
```

### 2.1.6 Keep duration - drop pdays & loan & default - 50:50
```{r Keep duration - drop pdays & loan & default - 50:50}
indxTrain50 <- createDataPartition(y = sampled_data$y,p = 0.50,list = FALSE)
sample_data_with_dur_3_dropped_50 <- sampled_data
sample_data_with_dur_3_dropped_50[, c('pdays', 'loan', 'default')] <- list(NULL)
training_with_dur_3dropped_col50 <- sample_data_with_dur_3_dropped_50[indxTrain50,]
testing_with_dur_3dropped_col50 <- sample_data_with_dur_3_dropped_50[-indxTrain50,]
```

### 2.1.7 Drop duration - drop pdays & loan & default - 50:50
```{r Drop duration - drop pdays & loan & default - 50:50}
sample_data_without_dur_3_dropped_50 <- sampled_data
sample_data_without_dur_3_dropped_50[, c('pdays', 'loan', 'default', 'duration')] <- list(NULL)
training_without_dur_3dropped_col50 <- sample_data_without_dur_3_dropped_50[indxTrain50,]
testing_without_dur_3dropped_col50 <- sample_data_without_dur_3_dropped_50[-indxTrain50,]
```

### 2.1.8 Keep duration - drop pdays & loan & default & emp.var.rate - 50:50
```{r Keep duration - drop pdays & loan & default & emp.var.rate - 50:50}
sample_data_with_dur_4_dropped_50 <- sampled_data
sample_data_with_dur_4_dropped_50[, c('pdays', 'loan', 'default', 'emp.var.rate')] <- list(NULL)
training_with_dur_4dropped_col50 <- sample_data_with_dur_4_dropped_50[indxTrain50,]
testing_with_dur_4dropped_col50 <- sample_data_with_dur_4_dropped_50[-indxTrain50,]
```

### 2.1.9 Drop duration - drop pdays & loan & default & emp.var.rate - 50:50
```{r Drop duration - drop pdays & loan & default & emp.var.rate - 50:50}
sample_data_without_dur_4_dropped_50 <- sampled_data
sample_data_without_dur_4_dropped_50[, c('pdays', 'loan', 'default', 'emp.var.rate', 'duration')] <- list(NULL)
training_without_dur_4dropped_col50 <- sample_data_without_dur_4_dropped_50[indxTrain50,]
testing_without_dur_4dropped_col50 <- sample_data_without_dur_4_dropped_50[-indxTrain50,]
```

### 2.1.10 Keep duration - drop pdays & loan & default - 80:20
```{r Keep duration - drop pdays & loan & default - 80:20}
indxTrain80 <- createDataPartition(y = sampled_data$y,p = 0.80,list = FALSE)
sample_data_with_dur_3_dropped_80 <- sampled_data
sample_data_with_dur_3_dropped_80[, c('pdays', 'loan', 'default')] <- list(NULL)
training_with_dur_3dropped_col80 <- sample_data_with_dur_3_dropped_80[indxTrain80,]
testing_with_dur_3dropped_col80 <- sample_data_with_dur_3_dropped_80[-indxTrain80,]
```

### 2.1.11 Drop duration - drop pdays & loan & default - 80:20
```{r Drop duration - drop pdays & loan & default - 80:20}
sample_data_without_dur_3_dropped_80 <- sampled_data
sample_data_without_dur_3_dropped_80[, c('pdays', 'loan', 'default', 'duration')] <- list(NULL)
training_without_dur_3dropped_col80 <- sample_data_without_dur_3_dropped_80[indxTrain80,]
testing_without_dur_3dropped_col80 <- sample_data_without_dur_3_dropped_80[-indxTrain80,]
```

### 2.1.12 Keep duration - drop pdays & loan & default & emp.var.rate - 80:20
```{r Keep duration - drop pdays & loan & default & emp.var.rate - 80:20}
sample_data_with_dur_4_dropped_80 <- sampled_data
sample_data_with_dur_4_dropped_80[, c('pdays', 'loan', 'default', 'emp.var.rate')] <- list(NULL)
training_with_dur_4dropped_col80 <- sample_data_with_dur_4_dropped_80[indxTrain80,]
testing_with_dur_4dropped_col80 <- sample_data_with_dur_4_dropped_80[-indxTrain80,]
```

### 2.1.13 Drop duration - drop pdays & loan & default & emp.var.rate - 80:20
```{r Drop duration - drop pdays & loan & default & emp.var.rate - 80:20}
sample_data_without_dur_4_dropped_80 <- sampled_data
sample_data_without_dur_4_dropped_80[, c('pdays', 'loan', 'default', 'emp.var.rate', 'duration')] <- list(NULL)
training_without_dur_4dropped_col80 <- sample_data_without_dur_4_dropped_80[indxTrain80,]
testing_without_dur_4dropped_col80 <- sample_data_without_dur_4_dropped_80[-indxTrain80,]
```


## 2.2 Training models and making predictions for all splits
### 2.2.1 Classify - Keep duration - drop pdays & loan & default - 70:30
#### Naive Bayesian
```{r Classify - Keep duration - drop pdays & loan & default - 70:30}
x <- training_with_dur_3dropped_col70[, -18]
y <- training_with_dur_3dropped_col70$y
model <- train(x, y, 'nb', trControl=trainControl(method='cv', number=10))
Predict <- predict(model, newdata = testing_with_dur_3dropped_col70)
confMatrix <- confusionMatrix(Predict, testing_with_dur_3dropped_col70$y,positive = "TRUE",mode = "prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

#### Decision Tree
```{r}
fit <- rpart(formula = y ~ .,data = training_with_dur_3dropped_col70,method = "class")
y_pred <- predict(fit,testing_with_dur_3dropped_col70,type = "class")
confMatrix <- confusionMatrix(y_pred,testing_with_dur_3dropped_col70$y,positive = "TRUE",mode="prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

### 2.2.2 Classify - Drop duration - drop pdays & loan & default - 70:30
#### Naive Bayesian
```{r Classify - Drop duration - drop pdays & loan & default - 70:30}
x <- training_without_dur_3dropped_col70[, -17]
y <- training_without_dur_3dropped_col70$y
model <- train(x, y, 'nb', trControl=trainControl(method='cv', number=10))
Predict <- predict(model, newdata = testing_without_dur_3dropped_col70)
confMatrix <- confusionMatrix(Predict, testing_without_dur_3dropped_col70$y,positive = "TRUE",mode = "prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

#### Decision Tree
```{r}
fit <- rpart(formula = y ~ .,data = training_without_dur_3dropped_col70[-16],method = "class")
y_pred <- predict(fit,testing_without_dur_3dropped_col70,type = "class")
confMatrix <- confusionMatrix(y_pred,testing_without_dur_3dropped_col70$y,positive = "TRUE",mode="prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

### 2.2.3 Classify - Keep duration - drop pdays & loan & default & emp.var.rate - 70:30
#### Naive Bayesian
```{r Classify - Keep duration - drop pdays & loan & default & emp.var.rate - 70:30}
x <- training_with_dur_4dropped_col70[, -17]
y <- training_with_dur_4dropped_col70$y
model <- train(x, y, 'nb', trControl=trainControl(method='cv', number=10))
Predict <- predict(model, newdata = testing_with_dur_4dropped_col70)
confMatrix <- confusionMatrix(Predict, testing_with_dur_4dropped_col70$y,positive = "TRUE",mode = "prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

#### Decision Tree
```{r}
fit <- rpart(formula = y ~ .,data = training_with_dur_4dropped_col70,method = "class")
y_pred <- predict(fit,testing_with_dur_4dropped_col70,type = "class")
confMatrix <- confusionMatrix(y_pred,testing_with_dur_4dropped_col70$y,positive = "TRUE",mode="prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

### 2.2.4 Classify - Drop duration - drop pdays & loan & default & emp.var.rate - 70:30
#### Naive Bayesian
```{r Classify - Drop duration - drop pdays & loan & default & emp.var.rate - 70:30}
x <- training_without_dur_4dropped_col70[, -16]
y <- training_without_dur_4dropped_col70$y
model <- train(x, y, 'nb', trControl=trainControl(method='cv', number=10))
Predict <- predict(model, newdata = testing_without_dur_4dropped_col70)
confMatrix <- confusionMatrix(Predict, testing_without_dur_4dropped_col70$y,positive = "TRUE",mode = "prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

#### Decision Tree
```{r}
fit <- rpart(formula = y ~ .,data = training_without_dur_4dropped_col70,method = "class")
y_pred <- predict(fit,testing_without_dur_4dropped_col70,type = "class")
confMatrix <- confusionMatrix(y_pred,testing_without_dur_4dropped_col70$y,positive = "TRUE",mode="prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

### 2.2.5 Classify - Keep duration - drop pdays & loan & default - 50:50
#### Naive Bayesian
```{r Classify - Keep duration - drop pdays & loan & default - 50:50}
x <- training_with_dur_3dropped_col50[, -18]
y <- training_with_dur_3dropped_col50$y
model <- train(x, y, 'nb', trControl=trainControl(method='cv', number=10))
Predict <- predict(model, newdata = testing_with_dur_3dropped_col50)
confMatrix <- confusionMatrix(Predict, testing_with_dur_3dropped_col50$y,positive = "TRUE",mode = "prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

#### Decision Tree
```{r}
fit <- rpart(formula = y ~ .,data = training_with_dur_3dropped_col50,method = "class")
y_pred <- predict(fit,testing_with_dur_3dropped_col50,type = "class")
confMatrix <- confusionMatrix(y_pred,testing_with_dur_3dropped_col50$y,positive = "TRUE",mode="prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

### 2.2.6 Classify - Drop duration - drop pdays & loan & default - 50:50
#### Naive Bayesian
```{r Classify - Drop duration - drop pdays & loan & default - 50:50}
x <- training_without_dur_3dropped_col50[, -17]
y <- training_without_dur_3dropped_col50$y
model <- train(x, y, 'nb', trControl=trainControl(method='cv', number=10))
Predict <- predict(model, newdata = testing_without_dur_3dropped_col50)
confMatrix <- confusionMatrix(Predict, testing_without_dur_3dropped_col50$y,positive = "TRUE",mode = "prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

#### Decision Tree
```{r}
fit <- rpart(formula = y ~ .,data = training_without_dur_3dropped_col50,method = "class")
y_pred <- predict(fit,testing_without_dur_3dropped_col50,type = "class")
confMatrix <- confusionMatrix(y_pred,testing_without_dur_3dropped_col50$y,positive = "TRUE",mode="prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

### 2.2.7 Classify - Keep duration - drop pdays & loan & default & emp.var.rate - 50:50
#### Naive Bayesian
```{r Classify - Keep duration - drop pdays & loan & default & emp.var.rate - 50:50}
x <- training_with_dur_4dropped_col50[, -17]
y <- training_with_dur_4dropped_col50$y
model <- train(x, y, 'nb', trControl=trainControl(method='cv', number=10))
Predict <- predict(model, newdata = testing_with_dur_4dropped_col50)
confMatrix <- confusionMatrix(Predict, testing_with_dur_4dropped_col50$y,positive = "TRUE",mode = "prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

#### Decision Tree
```{r}
fit <- rpart(formula = y ~ .,data = training_with_dur_4dropped_col50,method = "class")
y_pred <- predict(fit,testing_with_dur_4dropped_col50,type = "class")
confMatrix <- confusionMatrix(y_pred,testing_with_dur_4dropped_col50$y,positive = "TRUE",mode="prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

### 2.2.8 Classify - Drop duration - drop pdays & loan & default & emp.var.rate - 50:50
#### Naive Bayesian
```{r Classify - Drop duration - drop pdays & loan & default & emp.var.rate - 50:50}
x <- training_without_dur_4dropped_col50[, -16]
y <- training_without_dur_4dropped_col50$y
model <- train(x, y, 'nb', trControl=trainControl(method='cv', number=10))
Predict <- predict(model, newdata = testing_without_dur_4dropped_col50)
confMatrix <- confusionMatrix(Predict, testing_without_dur_4dropped_col50$y,positive = "TRUE",mode = "prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

#### Decision Tree
```{r}
fit <- rpart(formula = y ~ .,data = training_without_dur_4dropped_col50,method = "class")
y_pred <- predict(fit,testing_without_dur_4dropped_col50,type = "class")
confMatrix <- confusionMatrix(y_pred,testing_without_dur_4dropped_col50$y,positive = "TRUE",mode="prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

### 2.2.9 Classify - Keep duration - drop pdays & loan & default - 80:20
#### Naive Bayesian
```{r Classify - Keep duration - drop pdays & loan & default - 80:20}
x <- training_with_dur_3dropped_col80[, -18]
y <- training_with_dur_3dropped_col80$y
model <- train(x, y, 'nb', trControl=trainControl(method='cv', number=10))
Predict <- predict(model, newdata = testing_with_dur_3dropped_col80)
confMatrix <- confusionMatrix(Predict, testing_with_dur_3dropped_col80$y,positive = "TRUE",mode = "prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

#### Decision Tree
```{r}
fit <- rpart(formula = y ~ .,data = training_with_dur_3dropped_col80,method = "class")
y_pred <- predict(fit,testing_with_dur_3dropped_col80,type = "class")
confMatrix <- confusionMatrix(y_pred,testing_with_dur_3dropped_col80$y,positive = "TRUE",mode="prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

### 2.2.10 Classify - Drop duration - drop pdays & loan & default - 80:20
#### Naive Bayesian
```{r Classify - Drop duration - drop pdays & loan & default - 80:20}
x <- training_without_dur_3dropped_col80[, -17]
y <- training_without_dur_3dropped_col80$y
model <- train(x, y, 'nb', trControl=trainControl(method='cv', number=10))
Predict <- predict(model, newdata = testing_without_dur_3dropped_col80)
confMatrix <- confusionMatrix(Predict, testing_without_dur_3dropped_col80$y,positive = "TRUE",mode = "prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

#### Decision Tree
```{r}
fit <- rpart(formula = y ~ .,data = training_without_dur_3dropped_col80,method = "class")
y_pred <- predict(fit,testing_without_dur_3dropped_col80,type = "class")
confMatrix <- confusionMatrix(y_pred,testing_without_dur_3dropped_col80$y,positive = "TRUE",mode="prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

### 2.2.11 Classify - Keep duration - drop pdays & loan & default & emp.var.rate - 80:20
#### Naive Bayesian
```{r Classify - Keep duration - drop pdays & loan & default & emp.var.rate - 80:20}
x <- training_with_dur_4dropped_col80[, -17]
y <- training_with_dur_4dropped_col80$y
model <- train(x, y, 'nb', trControl=trainControl(method='cv', number=10))
Predict <- predict(model, newdata = testing_with_dur_4dropped_col80)
confMatrix <- confusionMatrix(Predict, testing_with_dur_4dropped_col80$y,positive = "TRUE",mode = "prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

#### Decision Tree
```{r}
fit <- rpart(formula = y ~ .,data = training_with_dur_4dropped_col80,method = "class")
y_pred <- predict(fit,testing_with_dur_4dropped_col80,type = "class")
confMatrix <- confusionMatrix(y_pred,testing_with_dur_4dropped_col80$y,positive = "TRUE",mode="prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

### 2.2.12 Classify - Drop duration - drop pdays & loan & default & emp.var.rate - 80:20
#### Naive Bayesian
```{r Classify - Drop duration - drop pdays & loan & default & emp.var.rate - 80:20}
x <- training_without_dur_4dropped_col80[, -16]
y <- training_without_dur_4dropped_col80$y
model <- train(x, y, 'nb', trControl=trainControl(method='cv', number=10))
Predict <- predict(model, newdata = testing_without_dur_4dropped_col80)
confMatrix <- confusionMatrix(Predict, testing_without_dur_4dropped_col80$y,positive = "TRUE",mode = "prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```

#### Decision Tree
```{r}
fit <- rpart(formula = y ~ .,data = training_without_dur_4dropped_col80,method = "class")
y_pred <- predict(fit,testing_without_dur_4dropped_col80,type = "class")
confMatrix <- confusionMatrix(y_pred,testing_without_dur_4dropped_col80$y,positive = "TRUE",mode="prec_recall")
confMatrix$overall['Accuracy']
confMatrix$byClass['Precision']
confMatrix$byClass['Recall']
confMatrix$byClass['F1']
confMatrix$table
```